One-stage point transect distance sampling using iterated integrated nested Laplace approximations

### 2019-11-28 paper-v2.tex
results finished

We fitted the models using penalised complexity priors for the hyperparameters of the GMRF \citep{simpson_penalising_2017}, setting $\mathbb{P}(\sigma > 2) = 0.01$ and $\mathbb{P}(\rho < 130) = 0.01$ where $\rho$ is the range of the Mat\'ern covariance.  The value of 130 was selected based on the minimum distance between sampling locations.  Full code for the analysis can be found in the Supplementary materials.

@@

Since CV values are influenced both by sampling effort and the magnitude of the estimated intensity means other methods we also map the lower and upper quantiles corresponding to a 95\% credible interval for each prediction cell (\autoref{fig:intensity-quantiles}).
\begin{figure}[!t]
	\includegraphics[scale=0.5]{figures/intensity_quantiles.png}
	\caption{The predicted posterior intensity summarised in three plots by the mean (upper),  0.025 quantile (lower left) and 0.975 quantile (lower right) for each prediction grid cell.  All three plots use a common colour scale}
	\label{fig:intensity-quantiles}
\end{figure}

@@

% POSTERIOR MATERN CORRELATION HERE
Add posterior matern correlation function

\begin{figure}[h]
	\includegraphics[scale=0.6]{figures/matern_posterior.png}
	\caption{Posterior Mat\'ern correlation function}
	\label{fig:half-normal}
\end{figure}

@@

@@

\begin{itemize}
	\item mini lit review - communicating uncertainty in spatial models w random effects
\end{itemize}

>>>>

We fitted the models using penalised complexity priors for the hyperparameters of the GMRF \citep{simpson_penalising_2017}, setting $\mathbb{P}(\sigma > 2) = 0.01$ and $\mathbb{P}(\rho < 130) = 0.01$ where $\rho$ is the range of the Mat\'ern covariance.  The value of 130 was selected based on the minimum distance between sampling locations.  Full code for the analysis can be found in the Supplementary materials.  Since only distance to observer was recorded we used the adjusted intensity given in \eqref{intensity-incomplete}.

@@

Since CV values are influenced both by sampling effort and the magnitude of the estimated intensity means other methods we also map the lower and upper quantiles corresponding to a 95\% credible interval for each prediction cell (\autoref{fig:intensity-quantiles}).
\begin{figure}[h]
	\includegraphics[scale=0.5]{figures/intensity_quantiles.png}
	\caption{The predicted posterior intensity summarised in three plots by the mean (upper),  0.025 quantile (lower left) and 0.975 quantile (lower right) for each prediction grid cell.  All three plots use a common colour scale}
	\label{fig:intensity-quantiles}
\end{figure}

@@

The posterior Mat\'ern correlation function is shown in \autoref{fig:matern-posterior}, the grey regions show the 95\% credible interval. 
\begin{figure}[h]
	\includegraphics[scale=0.6]{figures/matern_posterior.png}
	\caption{Posterior Mat\'ern correlation function}
	\label{fig:matern-posterior}
\end{figure}
This shows some correlation even at distances of 10,000 metres.  However, the northern-most and souther-most boundaries of the study region are approximately 8,000 metres apart.  The model is estimating positive correlation at distances further apart than were observed.  [[I'm not sure if this a problem??]]

@@

Finally, we note that the one-stage approach is a useful approach when it comes to representing uncertainty.  All plots here are based on sampling from the joint posterior of all model parameters.  As such they naturally average over the uncertainty in the detection model.

@@

\begin{itemize}
	\item mini lit review - communicating uncertainty in spatial models w random effects
	\item IDEA:  lots of papers don't even both themselves with uncertainty.  Could cite a bunch of recent ones, noting the search term in web of knowledge.
\end{itemize}
